%%
%% This is file `tikzposter-example.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% tikzposter.dtx  (with options: `tikzposter-example.tex')
%% 
%% This is a generated file.
%% 
%% Copyright (C) 2014 by Pascal Richter, Elena Botoeva, Richard Barnard, and Dirk Surmann
%% 
%% This file may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either
%% version 2.0 of this license or (at your option) any later
%% version. The latest version of this license is in:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% and version 2.0 or later is part of all distributions of
%% LaTeX version 2013/12/01 or later.
%% 








 \documentclass[25pt, a0paper, portrait, margin=0mm, innermargin=15mm,
     blockverticalspace=15mm, colspace=15mm, subcolspace=8mm]{tikzposter} %Default values for poster format options.

 \tikzposterlatexaffectionproofon %shows small comment on how the poster was made at bottom of poster

 % Commands
 \newcommand{\bs}{\textbackslash}   % backslash
 \newcommand{\cmd}[1]{{\bf \color{red}#1}}   % highlights command

 % Title, Author, Institute
 \title{Knowledge Distillation and its Variations}
 \author{Sandipan Mandal \& Teekam Chand Mandan}
 \institute{}

 % -- PREDEFINED THEMES ---------------------- %
 % Choose LAYOUT:  Default, Basic, Rays, Simple, Envelope, Wave, Board, Autumn, Desert,
 \usetheme{Autumn}
\usecolorstyle[colorPalette=BrownBlueOrange]{Germany}

\usepackage[backend=bibtex]{biblatex}
\addbibresource{cs698o_project.bib}

 \begin{document}

     \maketitle

     \begin{columns}%blocks will be placed into columns
         \column{.50}
         \block[]{Introduction}{In this project, we have implemented Knowledge Distillation(KD) from \cite{hinton2015distilling} and tried some variations of it. We evaluated the performance of KD on MNIST, notMNIST and SVHN datasets. Finally we have also implemented the paper Fitnets : Hints for Thin Deep Nets\cite{romero2014fitnets} and evaluated it on MNIST dataset.
            }
    
     \block[]{Knowledge Distillation}{In KD, we train a large teacher network \textbf{T}. We train our smaller student network \textbf{S} using a composite loss function consisting of two terms, one optimizing to improve label prediction accuracy, other to match pre-softmax logits with teacher \textbf{T}. Loss function is given by : $$L(W_S) = H(y_{true}, P_S) + \lambda H(P_T^{\tau}, P_S^{\tau})$$ where $H$ is the cross-entropy loss function, $y_{true}$ is the true label, $P_S$ is the softmax output of \textbf{S}, $P_T^{\tau}, P_S^{\tau}$ are respectively softmax output of \textbf{T} and \textbf{S} after dividing the corresponding logits by $\tau$.  }
     
  \block{Basic Adversarial Knowledge Distillation}{Here, we train a large teacher network \textbf{T} and smaller student network \textbf{S}. Using \textbf{T} and \textbf{S}, we train a discriinator network \textbf{D}, which can distinguish if a logit is constructed from \textbf{T} or \textbf{S}. We train our final student network \textbf{S} using a composite loss function consisting of two terms, one optimizing to improve label prediction accuracy, other to match pre-softmax logits with teacher \textbf{T}. The only difference here is that the logit matching is done adversarially using \textbf{D}. The loss function is given by : $$L(W_S) = \alpha H(y_{true}, P_S) - \beta H(network_{true} , P_D)$$ where $P_D$ is the softmax output of the disriminator network which is fed the student logit as input, $network_{true}$ gives whether the given logit comes from \textbf{T} or \textbf{S}. During training, the logit always comes from \textbf{S}. The other symbols are the same as earlier.}
  
  \block{Knowledge Distillation using GANs}{Here we generalize the approach we have taken earlier. It is based on GANs. Though it uses GANs,
the loss function we used is different from the one used by\cite{xu2017learning}. In this approach instead of pre-training the discriminator, we train discriminator, \textbf{D} and student network (generator), \textbf{G} on the go much like GANs. We assume the logits generated from \textbf{T} as \textbf{real} sample and the one generated from \textbf{S} as \textbf{fake} sample. The loss function for \textbf{D} is same as vanilla GAN, but for \textbf{G} which also happens to be student network has an additional term in it. $$L(W_D) = -\gamma[log(P_{real}(x)) + log(1-P_{fake}(x))]$$ $$L(W_G) = \beta H(y_{true}, P_S) - \alpha log(P_{fake}(x)) $$ where $P_{real}(x) = \sigma(D(T(x)))$ and $P_{fake}(x) = \sigma(D(G(x)))$, $\sigma()$ being sigmoid function.}
\block{Knowledge Distillation using Wasserstein GANs}{This aproach is exactly the same as the one above, except that here we use Wasserstein GANs (WGANs) instead of vanilla GANs. As a result the loss function is slightly different. The loss functions are:
$$L(W_D) = -\gamma[f_{real}(x) - f_{fake}(x)]$$ $$L(W_G) = \beta H(y_{true}, P_S) - \alpha f_{fake}(x) $$ where $f_{real}(x) = D(T(x))$ and $f_{fake}(x) = D(G(x))$}
%     \note[targetoffsetx=24cm, targetoffsety=-9cm,rotate=1,angle=270,radius=8cm,width=.75\textwidth,innersep=.4cm]{
%         You can place notes that are ``attached'' to the previous block using the command
%         \begin{quote} \texttt{\bs note[{\it options}]\{{\it contents}\}}\end{quote}
%         The note is placed by default slightly to the right of a ``target'' in the center of the previous block.  The note style may also allow for a connection between the note and the ``target''.  \\
%         The target may be shifted from the default by setting the options  \texttt{targetoffsetx, targetoffsety}, rotated by an angle with \texttt{rotate}, and its width with \texttt{width}.  The placement of the note in relation with the target is given in polar coordinates with \texttt{ radius, angle}. Please observe that notes are always drawn {\bf over} the other objects. They do not affect the placement of blocks.
%      }

     \column{.5}
         \block{Columns}{
              By default, blocks are arranged in a single column. If you want multiple columns for your poster, you may use the \texttt{columns} environment. For example,
             \begin{quote}
                 \texttt{\noindent \bs begin\{columns\}\\
                 \bs column\{.6\}\\
                 \bs block\{\dots\}\{\dots\}\\
                 \bs column\{.4\}\\
                 \bs block\{\dots\}\{\dots\}\\
                 \bs block\{\dots\}\{\dots\}\\
                 \bs end\{columns\}
                 }
             \end{quote}
             will create two columns of 60\% and 40\% the available width; spacing between successive columns is handled automatically.  The block command(s) following \texttt{\bs column} are the blocks to go in that column.  The number of columns is free to be chosen, but the relative widths must all be chosen.  If the widths sum to less than 1, empty space will be seen on the right.  If they sum to more than 1, the latter columns will be cut off.
         }

         \begin{subcolumns}
             \subcolumn{.45}
             \block{Subcolumns}{If you want to have an additional subdivision of columns inside a column, you may use the\\ \texttt{\bs subcolumns} environment inside of a column environment.  The functionality is similar to that of columns, but now the widths are relative to the width of the current column.}

             \subcolumn{.5}
             \block{}{An example use of subcolumns is.
                 \begin{quote}
                     \texttt{\bs begin\{subcolumns\}\\
                     \bs subcolumn\{.6\}\\
                     \bs block\{\dots\}\{\dots\}\\
                     \bs subcolumn\{.4\}\\
                     \bs block\{\dots\}\{\dots\}\\
                     \bs block\{\dots\}\{\dots\}\\
                     \bs end\{subcolumns\}
                     }
             \end{quote}
         }
         \end{subcolumns}

         \block[]{References}{\printbibliography[heading=none]}

     \end{columns}

%     \block[titleoffsety=-1cm,bodyoffsety=-1cm]{Sample document}{\vspace{2em}
%         This poster was created by the following commands (omitting the contents of the blocks and notes) to give a sense of how different objects are created and options used.
%         \begin{quote}
%             \texttt{\bs documentclass[25pt, a0paper, portrait, margin=0mm, innermargin=15mm,
%         blockverticalspace=15mm, colspace=15mm, subcolspace=8mm]\{tikzposter\}\\
%             \bs title\{Using tikzposter\} \bs author\{Pascal Richter, Elena Botoeva, Richard Barnard, \& Dirk Surmann\} \bs institute\{\}\\
%              \bs usetheme\{Autumn\}\bs usecolorstyle[colorPalette=BrownBlueOrange]\{Germany\}\\
%             \bs begin\{document\}\bs maketitle\\
%             \bs begin\{columns\} \bs column\{0.55\}\\
%             \bs block\{Creating the document\}\{The document\dots\} \bs note[targetoffsetx=-.05\bs textwidth,targetoffsety=9.5cm,innersep=.4cm,angle=-45,connection]\{\dots\}\\
%             \bs block\{The title matter\}\{The title\dots\}\\
%             \bs block\{Blocks\}\{Blocks are\dots\} \bs note[targetoffsetx=24cm, targetoffsety=-9cm,rotate=1,angle=270,radius=8cm,width=.75\bs textwidth,innersep=.4cm]\{You can\dots\}\\
%             \bs column\{0.45\} \bs block\{Columns\}\{By default,\dots\}\\
%             \bs begin\{subcolumns\} \bs subcolumn\{.45\}
%             \bs block\{Subcolumns\}\{If you\dots\}
%             \bs subcolumn\{.5\} \bs block\{\}\{An example\dots\}
%             \bs end\{subcolumns\}\\
%             \bs block[titlewidthscale=.8,bodywidthscale=.9,titleoffsety=9.5mm,bodyoffsety=9mm]\{Changing the Poster's Appearance\}\{If the default\dots\}
%             \bs end\{columns\}\\
%             \bs block[titleoffsety=-1cm,bodyoffsety=-1cm]\{Sample document\}\{This poster\dots\}\\
%             \bs end\{document\}
%             }
%         \end{quote}
%     }

 \end{document}




\endinput
%%
%% End of file `tikzposter-example.tex'.

